final_project_draft

### 2022-04-20 draft.Rmd
April 20th graded after class commit. Made a few changes and added some new visualizations.

ggplot(data = top10, aes(x = order, y = NetWorth, fill = Industry)) +
  geom_col(colour = "black") +
  coord_flip() +
  labs(x = " ", 
       y = "Net Worth",
       caption = "Measured in Billions",
       colour = "Industry",
       title = "2021 Forbes Billionaires with the Highest Net Worth") +
  scale_fill_viridis_d() +
  scale_x_discrete(labels = new_names2) +
  theme(legend.position = "bottom") +
  theme(axis.title = element_text(family = "mono",
                                  face = "bold",
                                  margin = margin(c(t = 30,
                                                    b = 30))),
        axis.text = element_text(family = "mono"),
        axis.text.y = element_text(face = "bold"),
        axis.ticks = element_blank(),
        plot.title = element_text(family = "mono",
                                  face = "bold",
                                  margin = margin(c(t = 15,
                                                    b = 15,
                                                    vjust = 15))),
        axis.title.x = element_text(vjust = -3),
        axis.title.y = element_text(vjust = 2),
        legend.margin = margin(c(t = 30, b = 30)),
        legend.title = element_text(family = "mono",
                                    face = "bold"),
        legend.text = element_text(family = "mono",
                                   face = "italic"),
        plot.caption = element_text(family = "mono",
                                    face = "italic",
                                    vjust = 35,
                                    hjust = 0.5,
                                    margin = margin(c(t = 30,
                                                      b = 30))),
        legend.key.size = unit(.3, 'cm'))
```

@@

ggplot(data = countries_10, aes(x = Country, y = age)) +
  geom_point(alpha = 0.4) +
  coord_flip() +
  geom_point(data = filter2, aes(x = order, y = Average, colour = "Mean Age of Billionaires"),
             size = 2.5) +
  scale_colour_manual(values = c("Mean Age of Billionaires" = "red")) +
  labs(x = "Country", 
       y = "Age",
       title = "Average Age of Billionaires by Country") +
  theme(legend.position = "bottom") +
  theme(axis.title = element_text(family = "mono",
                                  face = "bold"),
        axis.text = element_text(family = "mono"),
        plot.title = element_text(family = "mono",
                                  face = "bold"),
        axis.ticks = element_blank(),
        legend.title = element_blank(),
        legend.text = element_text(family = "mono",
                                   face = "italic"), 
        plot.caption = element_text(family = "mono",
                                    size = 9,
                                    face = "italic")) 
```

## Outliers labeled 
```{r}
ggplot(data = countries_10, aes(x = Country, y = age)) +
  geom_point(alpha = 0.4) +
  coord_flip() +
  geom_point(data = filter2, aes(x = order, y = Average, colour = "Mean Age of Billionaires"),
             size = 2.5) +
  scale_colour_manual(values = c("Mean Age of Billionaires" = "red")) +
  labs(x = "Country", 
       y = "Age",
       title = "Average Age of Billionaires by Country") +
  theme(legend.position = "bottom") +
  theme(axis.title = element_text(family = "mono",
                                  face = "bold"),
        axis.text = element_text(family = "mono"),
        plot.title = element_text(family = "mono",
                                  face = "bold"),
        axis.ticks = element_blank(),
        legend.title = element_blank(),
        legend.text = element_text(family = "mono",
                                   face = "italic"), 
        plot.caption = element_text(family = "mono",
                                    size = 9,
                                    face = "italic")) +
  geom_label_repel(data = check, aes(label = age))
```

@@

ggplot(data = above_or_below_us, aes(x = order, y = networth, colour = above_avg)) +
  geom_segment(aes(x = order, xend = order, y = avg, yend = networth)) +
  geom_point() +
  scale_colour_brewer(palette = "Accent") +
  coord_flip() +
  labs(x = " ",
      y = "Net Worth",
      caption = "Measured in Billions",
      colour = "Average",
      title = "Billionaires In The Fashion Industry",
      subtitle = "Do these billionaires fall above or below the average billionaire net worth in the U.S.?") +
  theme(axis.text = element_text(family = "mono"),
        axis.title = element_text(family = "mono"),
        legend.text = element_text(family = "mono"),
        legend.title = element_text(family = "mono",
                                    face = "bold"),
        plot.caption = element_text(family = "mono",
                                    hjust = 0.5),
        plot.title = element_text(family = "mono",
                                  face = "bold"),
        plot.subtitle = element_text(family = "mono",
                                     face = "italic"),
        axis.title.x = element_text(face = "bold"),
        axis.text.y = element_text(face = "italic",
                                   vjust = 1),
        axis.ticks = element_blank(),
        legend.box.background = element_rect()) 
```

@@

ggplot(data = country_30, aes(x = order, y = n)) +
  geom_point(colour = "orange") +
  geom_segment(aes(x = order, xend = order, y = 0, yend = n), colour = "blue", linetype = "dotdash") +
  coord_flip() +
  theme_light() +
  theme(axis.ticks.x = element_blank()) +
  labs(x = "Country", 
       y = "Count of Billionaires",
       title = "How Many Billionaires Are There From the Top 30 Countries?") +
  theme(plot.title = element_text(family = "mono"),
        axis.text = element_text(family = "mono"),
        axis.title = element_text(family = "mono"))

ggplot(data = country_30, aes(x = order, y = n, fill = n)) +
  geom_col(colour = "black") +
  coord_flip() +
  labs(x = " ", 
       y = " ",
       title = "How Many Billionaires Are There From the Top 30 Countries?",
       fill = "Count") +
  theme(plot.title = element_text(family = "mono",
                                  face = "bold"),
        axis.text = element_text(family = "mono"),
        axis.title = element_text(family = "mono"),
        legend.title = element_text(family = "mono",
                                    face = "bold"),
        legend.text = element_text(family = "mono",
                                   face = "italic"),
        axis.ticks = element_blank()) +
  scale_fill_viridis_b(n.breaks = 7) 
```

## Playing Around with New Variables - looking at self made billionaires, education level of billionaires 
```{r}
forbes_billionaires %>% select(Self_made, everything())
self_made <- forbes_billionaires %>% group_by(Self_made) %>%
  summarise(n = n()) %>%
  filter(!is.na(Self_made))

@@

ggplot(data = harvard, aes(x = Degree, y = NetWorth.x)) +
  geom_point() +
  coord_flip() +
  geom_label(data = harvard, aes(label = Name))

>>>>

ggplot(data = top10, aes(x = order, y = NetWorth, fill = Industry)) +
  geom_col(colour = "black") +
  coord_flip() +
  labs(x = " ", 
       y = "Net Worth",
       caption = "Measured in Billions",
       colour = "Industry",
       title = "2021 Forbes Billionaires with the Highest Net Worth") +
  scale_fill_viridis_d() +
  scale_x_discrete(labels = new_names2) +
  theme(axis.title = element_text(family = "mono",
                                  face = "bold",
                                  margin = margin(c(t = 30,
                                                    b = 30))),
        axis.text = element_text(family = "mono"),
        axis.text.y = element_text(face = "bold"),
        axis.ticks = element_blank(),
        plot.title = element_text(family = "mono",
                                  face = "bold",
                                  margin = margin(c(t = 15,
                                                    b = 15,
                                                    vjust = 15)),
                                  size = 15),
        axis.title.x = element_text(vjust = -3),
        axis.title.y = element_text(vjust = 2),
        legend.margin = margin(c(t = 30, b = 30)),
        legend.title = element_text(family = "mono",
                                    face = "bold",
                                    size = 8),
        legend.text = element_text(family = "mono",
                                   face = "italic",
                                   size = 8),
        plot.caption = element_text(family = "mono",
                                    face = "italic",
                                    vjust = 5,
                                    hjust = 0.5,
                                    margin = margin(c(t = 30,
                                                      b = 30))),
        legend.key.size = unit(.3, 'cm'))
```

@@

ggplot(data = countries_10, aes(x = Country, y = age)) +
  geom_point(alpha = 0.4) +
  coord_flip() +
  geom_point(data = filter2, aes(x = order, y = Average, colour = "Mean Age of Billionaires"),
             size = 2.5) +
  scale_colour_manual(values = c("Mean Age of Billionaires" = "red")) +
  labs(x = "Country", 
       y = "Age",
       title = "Average Age of Billionaires by Country") +
  theme(legend.position = "bottom") +
  theme(axis.title = element_text(family = "mono",
                                  face = "bold"),
        axis.text = element_text(family = "mono"),
        plot.title = element_text(family = "mono",
                                  face = "bold"),
        axis.ticks = element_blank(),
        legend.title = element_blank(),
        legend.text = element_text(family = "mono",
                                   face = "italic"), 
        plot.caption = element_text(family = "mono",
                                    size = 9,
                                    face = "italic"),
  legend.box.background = element_rect())
```

## Outliers labeled 
```{r}

countries10_2 <- countries_10 %>% mutate()

ggplot(data = countries_10, aes(x = Country, y = age)) +
  geom_point(alpha = 0.4, size = 1.5) +
  coord_flip() +
  geom_point(data = filter2, aes(x = order, y = Average, colour = "Mean Age of Billionaires"),
             size = 2.5, shape = 8) +
  scale_colour_manual(values = c("Mean Age of Billionaires" = "red")) +
  labs(x = "Country", 
       y = "Age",
       title = "Average Age of Billionaires by Country") +
  theme(legend.position = "bottom") +
  theme(axis.title = element_text(family = "mono",
                                  face = "bold"),
        axis.text = element_text(family = "mono"),
        plot.title = element_text(family = "mono",
                                  face = "bold"),
        axis.ticks = element_blank(),
        legend.title = element_blank(),
        legend.text = element_text(family = "mono",
                                   face = "italic"), 
        plot.caption = element_text(family = "mono",
                                    size = 9,
                                    face = "italic")) +
  theme(legend.position = "none") +
  geom_label_repel(data = check, aes(label = age)) +
  geom_text_repel(data = check, aes(label = Name, fontface = "bold"), size = 2) +
  geom_text_repel(data = check, aes(label = Source))
```

@@

ggplot(data = above_or_below_us, aes(x = order, y = networth, colour = above_avg)) +
  geom_segment(aes(x = order, xend = order, y = avg, yend = networth)) +
  geom_point() +
  scale_colour_brewer(palette = "Accent") +
  coord_flip() +
  labs(x = " ",
      y = "Net Worth",
      caption = "Measured in Billions",
      colour = "Average",
      title = "Billionaires In The Fashion Industry",
      subtitle = "Do these billionaires fall above or below the average billionaire net worth in the U.S.?") +
  theme(axis.text = element_text(family = "mono"),
        axis.title = element_text(family = "mono"),
        legend.text = element_text(family = "mono"),
        legend.title = element_text(family = "mono",
                                    face = "bold"),
        plot.caption = element_text(family = "mono",
                                    hjust = 0.5),
        plot.title = element_text(family = "mono",
                                  face = "bold",
                                  margin = margin(c(t = 10, b = 10))),
        plot.subtitle = element_text(family = "mono",
                                     face = "italic",
                                     margin = margin(c(t = 10, b = 10)),
                                     vjust = 2),
        axis.title.x = element_text(face = "bold",
                                    margin = margin(c(t = 10, b = 10))),
        axis.text.y = element_text(face = "italic"),
        axis.ticks = element_blank(),
        legend.box.background = element_rect()) 
```

@@

ggplot(data = country_30, aes(x = order, y = n)) +
  geom_point(colour = "orange") +
  geom_segment(aes(x = order, xend = order, y = 0, yend = n), colour = "blue", linetype = "dotdash") +
  coord_flip() +
  theme_light() +
  theme(axis.ticks.x = element_blank()) +
  labs(x = " ", 
       y = " ",
       title = "How Many Billionaires Are There From the Top 30 Countries?") +
  theme(plot.title = element_text(family = "mono"),
        axis.text = element_text(family = "mono"),
        axis.title = element_text(family = "mono")) +
  geom_text(aes(label = n, fontface = "bold", family = "mono"), hjust = -0.1, size = 3.2, colour = "black")

ggplot(data = country_30, aes(x = order, y = n, fill = n)) +
  geom_col(colour = "black") +
  coord_flip() +
  labs(x = " ", 
       y = " ",
       title = "How Many Billionaires Are There From the Top 30 Countries?",
       fill = "Count") +
  theme(plot.title = element_text(family = "mono",
                                  face = "bold"),
        axis.text = element_text(family = "mono"),
        axis.title = element_text(family = "mono"),
        legend.title = element_text(family = "mono"),
        legend.text = element_text(family = "mono"),
        axis.ticks = element_blank(),
        legend.position = "none") +
  scale_fill_viridis_b(n.breaks = 6) +
  geom_text(aes(label = n, fontface = "bold", family = "mono"), hjust = -0.1, size = 3, colour = "black")
```

## usa billionaires
```{r}
library(plotly)
us_forbes_billionaires <- combined_billionaires %>% filter(Country.x == "United States")
us_forbes_billionaires

us_forbes_billionaires %>% group_by(Industry) %>%
  summarise(n = n()) %>%
  arrange(desc(n))

plot10 <- ggplot(data = us_forbes_billionaires, aes(x = NetWorth.x, y = Age.x,
                                                    label = Name, colour = Industry)) +
  geom_jitter() +
  labs(x = "NetWorth",
       y = "Age",
       title = "Billionaires in the U.S.") +
  theme(plot.title = element_text(face = "bold",
                                  size = 15,
                                  margin = margin(c(t = 10, b = 10))),
        axis.ticks = element_blank(),
        legend.title = element_text(face = "bold"),
        axis.title = element_text(face = "bold"))

ggplotly(plot10, tooltip = "label")
```

## How many are self-made (from entire list) ? 
```{r}
forbes_billionaires %>% select(Self_made, everything())
self_made <- forbes_billionaires %>% group_by(Self_made) %>%
  summarise(n = n()) %>%
  filter(!is.na(Self_made))

@@

ggplot(data = harvard, aes(x = Degree, y = NetWorth.x)) +
  geom_point() +
  coord_flip()
